---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pinsha

<!-- badges: start -->
<!-- badges: end -->

The goal of pinsha is to provide an easy way to pin the actions in your github
workflows. 

## Installation

You can install the development version of pinsha like so:

``` r
pak::pak("zkamvar/pinsha")
```

## Example

This will take a github action string and replace the floating tag with an SHA
so that you can harden the security of your github actions.

```{r pin_action}
library("pinsha")
pin_action("r-lib/actions/check-r-package@v2")
pin_action("JamesIves/github-pages-deploy-action@v4.7.3")
```

You can find all of the third-party actions used with `pin_find_actions()`

```{r example}
# Actions in standard workflows
workflows <- system.file("workflows", package = "pinsha")
pin_find_actions(workflows)
```

To update all of the actions in your workflows, you can use the `pin()` command
from the root of your repository. Here, I am demonstrating on a temporary
copy of the directory: 

```{r, example-pin}
# pin() transforms all of the actions to use hashes
tmp <- tempfile()
fs::dir_copy(workflows, tmp)
pin(tmp, write = TRUE)
pin_find_actions(tmp)
```

